Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-03-03 ForegroundSimulations/ms.tex
Update figures on reflection specs
From 9ba1a46 (restructure):
==========================

(*) Update figures on reflection specs

@@

\subsection{Constraints on Reflections between Antennas}\label{sec:reflectometry}

Patra~et~al.~2015 (submitted) and Ewall-Wice~et~al.~2015 (submitted) discuss the measured and simulated reflections between a dish and its feed. We provide a related discussion by estimating the attenuation in power required to keep the foreground power reflected between adjacent antennas below the expected EoR H{\sc i} signal level for the different models of power patterns used in our study.

>>>>

Patra~et~al.~2015 (submitted) and \citet{ewa16} discuss the measured and simulated reflections between a dish and its feed. We provide a related discussion by estimating the attenuation in power required to keep the foreground power reflected between adjacent antennas below the expected EoR H{\sc i} signal level for the different models of power patterns used in our study.

@@
